\Title

### 2019-12-18 manuscript/manuscript.tex
Rename block-reduced data for block-median sources

\begin{table*}
    \begin{minipage}{80mm}
        \caption{
            Source distributions as combinations of source layouts and depth
            strategies.
        }
        \label{tab:source-distributions}
        \begin{tabular}{lccc}
            & Source bellow data & Block-reduced data & Grid sources \\ \hline
            Constant depth          & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
            Relative depth          & $\checkmark$ & $\checkmark$ & $\times$     \\
            Variable relative depth & $\checkmark$ & $\checkmark$ & $\times$     \\
        \end{tabular}
    \end{minipage}
\end{table*}

@@

>>>>

\begin{table*}
    \begin{minipage}{80mm}
        \caption{
            Source distributions as combinations of source layouts and depth
            strategies.
        }
        \label{tab:source-distributions}
        \begin{tabular}{lccc}
            & Source bellow data & Block-median sources & Grid sources \\ \hline
            Constant depth          & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
            Relative depth          & $\checkmark$ & $\checkmark$ & $\times$     \\
            Variable relative depth & $\checkmark$ & $\checkmark$ & $\times$     \\
        \end{tabular}
    \end{minipage}
\end{table*}

@@

\section{Discussion}
